%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Updated Deedy Resume
% Version 2.1 (05/16/2019)
%
% Author:
% Scott Lindauer (smlindauer@gmail.com)
% 
% Github:
% 
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\renewcommand{\sfdefault}{phv}
\newcommand*{\myfont}{\fontfamily{phv}\selectfont}

\documentclass[]{deedy-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{}{Scott Lindauer}{ 
\href{mailto:smlindauer@gmail.com}{smlindauer@gmail.com} | 919-270-7251 \\
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.250\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{\underline{Education}} 

\subsection{North Carolina}
\subsection{State University}
\descript{PhD, Physics}
\location{May 2019 | Raleigh, NC}
\sectionsep

\subsection{Clemson University}
\descript{BS, Physics; Minor, Math}
\location{May 2013 | Clemson, SC}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{\underline{Links}} 
http://bit.ly/scottlindauer \\
linkedin: \textbf{scottlindauer}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{\underline{Skills}}
\subsection{Programming}
\location{\textit{Over 10,000 lines:}}
Matlab \textbullet{} \LaTeX \\
\location{\textit{Over 1,000 lines:}}
Python \textbullet{} Labview \\ 
\location{\textit{Familiar:}}
C++ \textbullet{} Java \textbullet{} Shell \textbullet{} SAS \textbullet{} HTML \textbullet{} Mathematica\\
\sectionsep

\subsection{Lithography}
\location{Over 100 hours:}
Reactive Ion Etching \textbullet{} Photoresist Spinning \textbullet{} Contact Lithography \textbullet{} Barrel Ashing \\
\location{Familiar:}
Resistance Heated Evaporation \textbullet{} 6" Ebeam Evaporation
\sectionsep

\subsection{Microscopy}
\location{Over 1,000 hours:}
Brightfield \textbullet{} Darkfield \\
\location{Familiar:}
SEM \textbullet{} AFM \textbullet{} STM \\
Fluorescence \\
\sectionsep

\subsection{Microfluidics}
\location{Over 1,000 hours:}
Polystyrene Spheres \textbullet{} E. coli\\
\location{Over 100 hours:}
SU-8 Colloids \textbullet{} PIV \\
\location{Familiar:}
DNA \textbullet{} S. Epidermidis \\
\sectionsep

\subsection{Chemistry}
\location{Over 100 hours:}
PDMS \textbullet{} Piranha \\
RCA Cleaning \textbullet{} LPCVD \\
Buffer Synthesis \\
\location{Familiar:}
Lipid Extrusion \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage}
\hfill
\vline
\hfill
\begin{minipage}[t]{0.720\textwidth} 

\vspace{5pt}
Scott Lindauer is passionate about colloidal, granular, computational, and biological physics. He possesses experience in numerous areas, including microfluidics, photolithography, programming, image analysis, microscopy, chemistry, and bacteria cultivation.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{\underline{Graduate Research}}
\runsubsection{North Carolina State University: Physics Department} \\
\descript{Graduate Research Assistant}
\location{Jan 2015 – Present | Raleigh, NC}
Worked with Prof Karen Daniels and Prof Robert Riehn on microfluidic experiments, in order to extend our understanding of dense granular, colloidal, and bacterial solids.

\begin{enumerate}[label=\textbullet,leftmargin = !,labelindent = -15pt, itemindent = 0pt, noitemsep, topsep = 0pt]

\item Designed, fabricated, and conducted experiments with microfluidic devices, which formed flow-stabilized solids out of colloids and bacteria. 

\item Determined that colloidal size affects the critical formation velocity, colloidal solids transition from thermal to athermal behavior at high velocities, and confined colloidal solids do not follow the Carmen-Kozeny permeability model.

\item Determined that the formation flow-stabilized solids with motile (active) matter is possible, the bacterial solids only form at higher velocities than passive colloids of equivalent size, and that bacterial cell division inside the solid increases the solid size and particle density.

\end{enumerate}

\vspace{5pt}

\location{May 2014 – Dec 2014 | Raleigh, NC}
Worked with Prof Karen Daniels to repair, maintain, improve, and conduct experiments an experimental air table, which creates a frictionless surface for granular experiments. 

\begin{enumerate}[label=\textbullet,leftmargin = !,labelindent = -15pt, itemindent = 0pt, noitemsep, topsep = 0pt]

\item Modified the air table to create experimentally simulated microgravity in a granular packing, similar to rubble-pile asteroids.

\item Determined that slow moving, thin, and flexible diggers are the most advantageous for sampling missions on rubble-pile asteroids.

\item This work was instrumental in the continuation of our lab's granular asteroid projects, including the funding of the NASA EMPANDA project and continued experimentation which included the use of parabolic flights to further simulate microgravity.

\end{enumerate}

\section{\underline{Undergraduate Research}}

\runsubsection{Clemson University: Physics Department}
\descript{| Undergraduate Researcher}
\location{August 2010 - May 2013 | Clemson, SC}
Worked with Prof Murray Daw to complete an honors senior thesis in physics.

\begin{enumerate}[label=\textbullet,leftmargin = !,labelindent = -15pt, itemindent = 0pt, noitemsep, topsep = 0pt]

\item Numerically simulated the motion of an electron about a hydrogen atom through a Stern-Gerlach apparatus using a non-standard approach to quantum mechanics.

\item Verified that the initial conditions of the electron effect the final outcome of its location, velocity, and spin.

\end{enumerate}

\sectionsep

\runsubsection{Clemson University: Physics Department} 
\descript{| Lead Project Manager}
\location{August 2012 - May 2013 | Clemson, SC}
Worked with Prof Chad Sosolik in collaboration with the Society of Physics Students (SPS) chapter of Clemson University to design an on-site cyclotron and budgeted the procurement of materials need for fabrication.

\begin{enumerate}[label=\textbullet,leftmargin = !,labelindent = -15pt, itemindent = 0pt, noitemsep, topsep = 0pt]

\item Co-wrote an undergraduate research grant which successfully funded the project.

\end{enumerate}

% \runsubsection{ELETTRA Synchrotron} \\
% \descript{| Undergraduate Student}
% \location{June 2011 - July 2011 | Trieste, Italy}
% Worked with Prof Peter Barnes on spectroscopy experiments involving surface physics. Attended comprehensive lectures at the ELETTRA Synchrotron Light Laboratory.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%	  PUBLICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{\underline{Publications}}
\runsubsection{}
\begin{flushleft}
\begin{enumerate}[noitemsep]
\item\textbf{Scott Lindauer}, Karen E. Daniels, Robert Riehn. \textit{Formation of Active, Living Flow-Stabilized Solids}, In Preparation. 2019.

\item\textbf{Scott Lindauer}, Carlos Ortiz, Robert Riehn, Karen E. Daniels. \textit{Particle Size Effects in Flow-Stabilized Colloidal Solids}, In Preparation. 2019.

\item Jonathan E. Kollmer, \textbf{Scott Lindauer}, and Karen E. Daniels. \textit{Digging on Asteroids: a Laboratory Model of Granular Dynamics in Microgravity}, ASCE Proc. for Earth \& Space Conf. 2016.
\end{enumerate}
\end{flushleft}

\end{minipage} 

\pagebreak

\begin{minipage}[t]{.90\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     TEACHING EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{\underline{Teaching Experience}}

\runsubsection{North Carolina State University} 
\descript{| Teaching Assistant}
\location{August 2017 - December 2018 | Raleigh, NC}
Taught a senior physics lab course, which included digital electronic projects and laboratory experiments of modern physics experiments.

\begin{enumerate}[label=\textbullet,leftmargin = !,labelindent = -15pt, itemindent = 0pt, noitemsep, topsep = 0pt]

\item Taught undergraduates to analyze data in Python, work in a cleanroom, use microscopy setups, cultivate bacterial cultures of E. coli, and to analyze the thermal motion of colloids and bacteria.

\vspace{5pt}

\end{enumerate}

\location{August 2013 - December 2014 | Raleigh, NC}
Taught a mechanics lab for undergraduate physics students, which included a lecture session and subsequent experimentation on the topic.

\begin{enumerate}[label=\textbullet,leftmargin = !,labelindent = -15pt, itemindent = 0pt, noitemsep, topsep = 0pt]

\item Oversaw all other graduate teaching assistants in the last semester of being a teaching assistant. Taught other graduate students how to lecture and run the experiments and managed any outstanding issues which arose in the lab classes.

\end{enumerate}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PRESENTATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\underline{Presentations}}
\runsubsection{}
\begin{flushleft}
\begin{enumerate}
\item\textbf{\textit{Particle Size Efects in Flow-Stabilized Colloidal Solids}}. Poster. Triangle Soft Matter Workshop, Chapel Hill, NC, 2017.

\item\textbf{\textit{Particle Size Effects in Flow-Stabilized Colloidal Solids}}. Talk. APS March Meeting, New Orleans, LA, 2017.

\item\textbf{\textit{Particle Size Effects in Heaps of Spherical Colloids}}. Poster. Gordon Research Conference, Easton, MA, 2016.

\item\textbf{\textit{Particle Size Effects in Heaps of Spherical Colloids}}. Poster. Triangle Soft Matter Workshop, Durham, NC, 2016.

\item\textbf{\textit{Thermal Behavior in Heaps of Spherical and Shaped Colloids}}. Talk. APS March Meeting, Baltimore, MD, 2016.

\item\textbf{\textit{Drilling into Granular Asteroids: Modeling Penetration of Granular Materials in Microgravity}}. Poster. Pan-American Advanced Study Institute, La Plata, Argentina, 2014.
\end{enumerate}
\end{flushleft}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LEADERSHIP
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{\underline{Leadership}}
\runsubsection{}
\begin{flushleft}
\begin{tabular}{p{.2\textwidth}p{.80\textwidth}}
\textbf{Aug 2015 - July 2016}    &   \textbf{Past President of the Graduate Physics Student Association} at North Carolina State University: I advised the next GPSA administration on the operations and protocols required to successfully interact with graduate student governance and continue to reinvigorate the GPSA student population. This advisory role has continued beyond the end of the Past President position in July 2016.\\
\textbf{Aug 2014 - July 2015}	&	\textbf{President of the Graduate Physics Student Association} at North Carolina State University: I directed the GPSA governing body and renewed efforts to rejuvenate the graduate physics population's internal socialization in order to increase the overall health and cohesion of all graduate students. \\
\textbf{Aug 2012 - May 2012}	&	\textbf{Vice President of the Society for Physics Students} at Clemson University: I worked as the intermediary between undergraduate physics students and the physics department's administration and professors. I collaborated with the physics department to begin building a cyclotron. \\
\end{tabular}
\end{flushleft}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SCHOLARSHIPS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{\underline{Scholarships}}
\runsubsection{}
\begin{flushleft}
\begin{tabular}{rll}
\textbf{Dec 2018}    &   Awarded North Carolina State University Doctoral Dissertation Completion Grant \\
\textbf{Jan 2015}	&	Awarded RT-MRSEC Fellowship Award \\
\textbf{June 2014}	&	Awarded North Carolina Space Grant Scholarship \\
\textbf{Jan 2013}	&	Inducted as a Member of Sigma Pi Sigma, Physics Honors Society \\
\end{tabular}
\end{flushleft}
\end{minipage}

\end{document} 
